A general Nullstellensatz for generalized spaces

### 2023-06-29 paper-qcoh.tex
typo (closing #4)

\begin{rem}The finite presentability condition in
Lemma~\ref{lemma:fp-double-dual} cannot be dropped. For instance, in the case
that~$\TT$ is the theory of commutative rings with unit and~$A$ is the
ring~$\QQ$ of integers, we have~$\Spec(A^\sim) \cong \Spec(0^\sim)$, where~$0$
is the zero ring, as~$\QQ$ allows ring homomorphisms only in those finitely
presented rings in which~$1 = 0$ holds. Hence~$A^\sim$
and~$(U_\TT)^{\Spec(A^\sim)} \cong (U_\TT)^{\Spec(0^\sim)} \cong 0^\sim$ do not coincide.
\end{rem}

>>>>

\begin{rem}The finite presentability condition in
Lemma~\ref{lemma:fp-double-dual} cannot be dropped. For instance, in the case
that~$\TT$ is the theory of commutative rings with unit and~$A$ is the
ring~$\QQ$ of rational numbers, we have~$\Spec(A^\sim) \cong \Spec(0^\sim)$, where~$0$
is the zero ring, as~$\QQ$ allows ring homomorphisms only to those finitely
presented rings in which~$1 = 0$ holds. Hence~$A^\sim$
and~$(U_\TT)^{\Spec(A^\sim)} \cong (U_\TT)^{\Spec(0^\sim)} \cong 0^\sim$ do not coincide.
\end{rem}
